%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Eugene K.}{Lee}
\position{Master of Public Health{\enskip\cdotp\enskip}Student}
\address{Placeholder}

\mobile{(+1) Placeholder}
\email{21el9@queensu.ca}
%\dateofbirth{January 1st, 1970}
\homepage{https://www.obfuscatory.dev}
\github{https://github.com/ekjl}
% \linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Infection Prevention and Control}
  {(Organization)\\(Street Address)\\(City, province, postal code)}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application for IPAC Practicum}
% How the letter is opened
\letteropening{Dear contact,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Resume}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Eugene K. Lee~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am currently undergoing a Masters of Public Health with an IPAC specialization, with aspirations toward field epidemiology and IPAC within hospital settings. My personal interests reside in enhancing obsolete patient management systems in patient care settings with modern communication technologies in order to optimize health care surveillance and delivery. As an advocate of digital privacy during the modern era of invasive surveillance, my passion lies in retaining maximum privacy while recognizing the tangible value of surveillance. Ultimately, my long-term intent consolidates my knowledge of computers and digital privacy with the experiences I gain in health care to help contribute to the field in a novel way.

% \lettersection{Why ?}

\lettersection{Qualifications}
The MPH-IPAC graduate program provides training in three main areas: Skills in literature review specifically applicable to public health, knowledge in program planning and evaluation through learned frameworks and epidemiological methods, and the breadth of IPAC responsibilities encountered in hospital settings. In addition to the aforementioned academic training, my previous work in hospital patient care as a student nurse and further experience in business-to-business support and retail have afforded me experience in administrative skills, data management, and communication. Although my academic degree relates to health, I am proficient with computers, in both hardware and software. If specialized software is utilized in the workplace, I have the highest confidence in my ability to quickly gain familiarity with the tool. I have encountered highly fragmented toolsets during my experience in B2B support and hospitals, and have had no issue with gaining proficiency in a short period of time.

\lettersection{Closing}
Thank you for your time. Given the opportunity, I am confident I can exceed your expectations. If any further information is required, please do not hesitate to ask.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
